Exploring probability distributions for bivariate temporal granularities

### 2020-01-30 main.Rmd
all kables removed in smart meter section

smart_meter <- sm %>% as_tsibble() %>% dplyr::select(customer_id, 
                              reading_datetime, 
                              general_supply_kwh, 
                              everything()) %>% head()

knitr::kable(smart_meter, format = "markdown")
```

@@

```{r search, echo=TRUE}
library(gravitas)
smart_smart_search <- smart_meter %>% search_gran()
knitr::kable(smart_smart_search, format = "markdown")
```

@@

```{r search_limit1, echo=TRUE}
smart_meter_limit1 <- smart_meter10 %>% 
  search_gran(highest_unit = "month")
knitr::kable(smart_meter_limit1, format = "markdown")
```

@@

```{r search_gran_limit2, echo=TRUE}

smart_meter_limit2 <- smart_meter10 %>% search_gran(highest_unit = "month",
                              filter_out = c("hhour", "fortnight")
)
knitr::kable(smart_meter_limit2, format = "markdown")
```

>>>>

smart_meter <- sm %>% as_tsibble() %>% dplyr::select(customer_id, 
                              reading_datetime, 
                              general_supply_kwh, 
                              everything()) %>% head()
smart_meter
# knitr::kable(smart_meter, format = "markdown")
```

@@

```{r search, echo=TRUE}
library(gravitas)
smart_meter %>% search_gran()
#smart_smart_search <- smart_meter %>% search_gran()
#knitr::kable(smart_smart_search, format = "markdown")
```

@@

```{r search_limit1, echo=TRUE}
smart_meter10 %>% 
  search_gran(highest_unit = "month")
# smart_meter_limit1 <- smart_meter10 %>% 
#   search_gran(highest_unit = "month")
# knitr::kable(smart_meter_limit1, format = "markdown")
```

@@

```{r search_gran_limit2, echo=TRUE}
smart_meter10 %>% search_gran(highest_unit = "month",
                              filter_out = c("hhour", "fortnight")
                              )
# smart_meter_limit2 <- smart_meter10 %>% search_gran(highest_unit = "month",
#                               filter_out = c("hhour", "fortnight")
# )
# knitr::kable(smart_meter_limit2, format = "markdown")
```
